When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-04-02 presentation/inbreeding.Rmd
Nearly finished with all slides

## Acknowledgements

@@

>>>>

**Coauthors**

- [Greta Bocedi](https://www.abdn.ac.uk/sbs/people/profiles/greta.bocedi)
- [Ryan Germain](http://ryanrgermain.wixsite.com/ecol-evol)
- [Aline Lee](https://www.ntnu.edu/employees/aline.m.lee)
- [Jane Reid](https://www.abdn.ac.uk/ibes/profiles/jane.reid)
- [Matthew Wolak](https://matthewwolak.github.io/)

**Maxwell computing cluster**

- Naveed Khan

![](images/leverhulme.png)

![](images/LOGO-ERC.jpg)

<br>
![](images/aberdeen.png)

![](images/UoS_logo.png)

@@

<span style="font-size: 14px;">
Duthie, AB & JM Reid (2015) *PLoS One* [10:e0125140](https://bradduthie.github.io/Duthie%26Reid2015.pdf) [SI](https://bradduthie.github.io/Duthie%26Reid2015SI.pdf); Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf) [A1](https://bradduthie.github.io/Duthie_Reid2016_AppendixA.pdf) [A2](https://bradduthie.github.io/Duthie_Reid2016_AppendixB.pdf) [SI](https://bradduthie.github.io/Duthie_Reid2016_SM.pdf); Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf) [SI-1](https://bradduthie.github.io/DuthieEtAl2016_SI1.pdf) [SI-2](https://bradduthie.github.io/DuthieEtAl2016_SI2.pdf); Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2017_SI.pdf);  Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf) [SI](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf)
</span>
